An improved platform for Web service wrapping, discovery and consumption

### 2010-06-13 trunk/papers/icsoc2010/paper.tex
changes in introduction
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@842 d8b0c59b-6544-0410-94d9-83a5658a058e

The remainder of this paper is organised as follows. Section 2 covers the state of the art in web services publication, discovery and wrapping/consumption. Section 3 describes our platform for publishing web services and empowering end-users to discover services. Next, in Section 4 we present how we tackle with the web services wrapping, available possibilies and limitations. Section 5 gives the reader a clearer use case and how this work is integrated into the FAST platrofmr, and finally, we present our main conclusions and highlight future lines of research in Section 6.

>>>>

The remainder of this paper is organised as follows. Section 2 covers the state of the art in web services publication, discovery and wrapping/consumption. In Section 4 we present how we tackle with the web services wrapping, available possibilies and limitations. Next, section 3 describes our platform for publishing web services and empowering end-users to discover services. Section 5 gives the reader a clearer use case and how this work is integrated into the FAST platrofmr, and finally, we present our main conclusions and highlight future lines of research in Section 6.
